\section{Achievements of Research Aims \& Objectives}

\subsection{Aim of the Project}

\textit{The aim of this research is to design, develop and evaluate a toolkit to help system operators to reduce the \ac{mttr} when the system is experiencing an anomaly. This will be achieved by using machine learning models to investigate all the services in the system and highlighting the most probable root causes in order, So the operators don’t have to find a needle in a haystack.} The aim of the project was successfully achieved by designing, developing, and evaluating a flexible framework which interchangeable components. This makes it easy for the data scientist to create reliable machine learning models to find root causes of anomalies, which in turn help system operators to reduce the \ac{mttr}.


\subsection{Research Objectives}

\begin{longtable}{|p{40mm}|p{91mm}|p{20mm}|}
    \hline
    \textbf{Research Objective} & \textbf{Justification} & \textbf{Status} \\ \hline
    Problem identification & A project with proper scope was identified to research on. & Completed \\ \hline
    Literature review & A thorough literature survey was done on all the related topics. & Completed \\ \hline
    Developing an evaluation framework & \href{https://github.com/MrSupiri/MicroSim}{MicroSim} was developed and published. & Completed \\ \hline
    Data gathering and analysis & \ac{ebpf} agent \ac{gazer} and data preprocessor \ac{sherlock} was developed. & Completed \\ \hline
    Developing encoding method & \ac{sherlock} uses RGB color scheme to represent telemetry data. & Completed \\ \hline
    Developing the model & An autoencoder was developed to detect anomalies. & Completed \\ \hline
    Testing and evaluation & Both functional and non functional testing was done in order to verify the project’s capabilities. Along with third party evaluation. & Completed \\ \hline
    Integration & \ac{lazy-koala-operator} was built to bind up all the components togather. & Completed \\ \hline
    \caption{Achievements of Research Objectives(self-composed)}
  \end{longtable}
  
  