\section{Evaluation Criteria}

As mentioned in section \ref{sec:evaluation-methodology}, the author conducted many interviews with experts in the field. Prior to each interview, the author got the consent of the evaluators to record the session. The following criteria were based on the themes extracted from the transcript of those interviews.

\begin{longtable}{|p{33mm}|p{120mm}|}
    \hline
    \textbf{Criteria} &
    \textbf{Purpose} \\ \hline
    Overall impression about the project and research gap &
        Even Though cloud computing is a very matured field \ac{aiops} is still at its earliest stage. Therefore, validating the end for this research is critical to show the value addition done by this research. \\ \hline
    Research scope and depth &
        In the author's opinion, the project had a very ambitious scope attached to it. Seeing an outside perspective to this will further validate the contributions made from the project. \\ \hline
    Design and architecture &
        Since this project forces on microservices systems, the project itself was implemented as microservices, and getting a microservices specification just right is a complicated process. \\ \hline
    Prototype implementation &
        As this meant to be a lightweight monitoring solution, it should have a minimal impact on the existing system. All the components were carefully constructed to minimize the resources wastage as possible. Getting an expert opinion on these design decisions will add more credibility to the author's claims. \\ \hline
    Platform usability &
        As a plug and play system, it should be fairly easy for anyone with basic knowledge of Kubernetes to get it working within their system. \\ \hline
    Contribution to the Domain &
        Validate the value addition done by the project and what it could mean for the future of \ac{aiops}. \\ \hline
    Future work &
        Getting experts' opinions to see whether there are any implications on this project outside of being merely a research project. This will help to confirm the author’s main goal of this system is based on whether future research will be achieved or not. \\ \hline
  
    \caption{Evaluation Criteria (self-composed)}
\end{longtable}