\chapter*{Acknowledgement}

The completion of this research was an arduous journey, but it was also a fantastic learning opportunity. I am very lucky to be surrounded by inspiring people throughout my journey. I am grateful to a number of people who made my journey a special one.
Without the advice and support of those who were there to reach out and help me to shine, I would not have been able to accomplish this research.

First of all, Mr. Guhanathan Poravi, my project supervisor, deserves a very special appreciation for helping me grasp what computer science research entailed, Kudos to him for guiding and instructing me through my path of success. It was his guidance and support that built my confidence and pushed me to ignite my highest potential with passion in learning. I would also like to express my gratitude to all the lecturers at the Informatics Institute of Technology for providing all the knowledge without any hesitation from the beginning of the degree programme. In extend to that, a very special thanks goes out to Jacob Payne, my Google Summer of Code mentor. He was the one who guided me through the ways of Kubernetes development and Matthias Rampke, who helped me in identifying the problem domain and building the scope of the project. 

A special thanks goes out to all of the industry and academic experts who sacrificed their time to listen to my research presentations and provide feedback during requirement gathering and evaluation interviews for this research project. And finally, I have to thank my friends for encouraging me and motivating me during my difficult times and also to the seniors for their valuable feedback and assistance throughout the project. At Last but not least, I would like to thank my beloved parents for being patient and encouraging during all my ups and downs; Without you none of this would have been possible. 







