\section{SLEP Issues and Mitigation}\label{sec:slep}



\begin{longtable}{|p{78mm}|p{78mm}|}
    \hline

    \textbf{Social} & \textbf{Legal} \\ \hline
    During both the requirement elicitation phase and evaluation phase several interviews were carried out. To provide credibility to the author's claims it was decided to include the interviewee's name. Prior to including their names, the author reached out and got their written consent and only included the names of those who have agreed to publish their name along with this research project. & In order to simplify the development, a number of open-source libraries and tools were used. All the licenses that came with those were properly cited within the code base along with references to original sources. Finally, it was decided to publicize this project under the MIT licenses as well as a token of gratitude to the FOSS community. \\ \hline

    \textbf{Ethical} & \textbf{Professional} \\ \hline
    One of the most prominent ethical issues that come up during the research process is plagiarism. To prevent this all the literature used to compile this document was properly cited. On the implementation side, even the smallest code snippets that were taken from a third-party source were properly cited to the original sources in order to provide the credit where credits are due. & Since this project is meant to be extended by other researchers, implementation was done following software engineering best practices such as code commenting and generalizations. Additionally, the testing and the evaluation of the project were done with a system that closely resembles the real-world scenarios and the collected data was present without any manipulation. \\ \hline

    \caption{SLEP issues and mitigations (self-composed)}
\end{longtable}
